---
title: "Political Social Media and Climate Change Concern: Evidence from Latin America"
author: "Breno A. H. Marisguia"
format: html
server: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.align='center')

library(pacman)
pacman::p_load(
  shiny, haven, tidyverse, broom, broom.mixed, ggplot2, ggeffects, ggokabeito,
  ggridges, plotly, directlabels, lme4
  )

load("lp.RData")
```

::: {html}
<style>
p {
    text-align: justify !important;
}
</style>
:::

## Preface
The urgency of climate adaptation and disaster risk management extends beyond scientific models and policy frameworks — it demands active public engagement, institutional coordination, and informed decision-making at all levels of governance. In Latin America — and especially Brazil — where climate-related vulnerabilities are increasingly pronounced, municipal governments serve as the frontline actors in building resilience and implementing adaptive strategies. However, their effectiveness is shaped not only by technical capacity but also by societal perceptions of climate risk, political dynamics, and the growing influence of digital information ecosystems. Understanding how public concern about climate change is shaped in this complex landscape is essential for fostering policies that are both evidence-based and socially grounded.

This work has been undertaken as both a scholarly investigation and a demonstration of my expertise in climate change perception, political communication, and applied social research. By combining quantitative data analysis with theoretical insights on media influence and ideology, this study showcases my ability to conduct rigorous empirical research with direct policy relevance. It also aligns with the objectives of the **Programa Adapta**, which seeks to strengthen institutional competencies for disaster risk management, adaptation, and climate resilience in Brazilian municipalities.

The role of Pesquisador Pleno in this project requires not only expertise in socio-environmental research but also the ability to engage with policymakers, analyze governance structures, and develop data-driven strategies for climate adaptation. This study exemplifies my ability to synthesize climate science and public opinion analysis to produce actionable insights — an approach that is critical for supporting municipal governments in strengthening climate governance. Beyond its academic contributions, this research reflects my commitment to addressing real-world climate challenges, integrating interdisciplinary perspectives, and producing knowledge that informs adaptation strategies, governance frameworks, and public engagement efforts.

## 1. Introduction

Climate change is widely recognized as one of the most pressing global challenges, affecting environmental, economic, and social systems worldwide. Latin America, a region highly vulnerable to climate-related hazards such as extreme weather events, droughts, and biodiversity loss, faces significant risks from global warming (Azócar et al., 2020). Despite the severity of the issue, public perception and concern about climate change vary across countries and demographic groups, influenced by factors such as education, political ideology, and media exposure (Evans & Zechmeister, 2018; Spektor, Fasolin, & Camargo, 2023). Understanding these variations is crucial for developing effective climate policies and communication strategies in the region.

Public opinion plays a significant role in shaping governmental responses to climate change, as citizen attitudes can drive policy adoption and environmental governance (Fairbrother, 2022; Dasgupta & De Cian, 2018). In Latin America, studies suggest that there is generally high concern about climate change, with majorities in most countries acknowledging its severity and human origins (Spektor, Fasolin, & Camargo, 2023). However, the extent of concern can be modulated by socioeconomic status, political ideology, and access to reliable information (Gómez-Casillas & Márquez, 2023). Notably, misinformation and ideological divides have contributed to climate skepticism, which can hinder collective action (Lewandowsky, Gignac, & Oberauer, 2013).

In recent years, social media has emerged as a dominant platform for information dissemination, influencing public awareness and engagement with climate issues (Diehl et al., 2024; Shah, 2024). While some scholars argue that social media fosters environmental awareness by providing access to scientific knowledge and mobilizing activism (Gómez-Casillas & Márquez, 2023), others highlight its role in amplifying misinformation and creating echo chambers that reinforce pre-existing beliefs (Tyagi & Carley, 2021). The extent to which exposure to political information through social media affects climate change concern in Latin America remains an open question, requiring further empirical analysis.

This study aims to investigate the relationship between exposure to political content via social media and climate change perception in Latin America, drawing on data from the 2023 Latin American Public Opinion Project (LAPOP) to answer if this exposure increase the likelihood of perceiving climate change as a serious threat, and to what extent is this effect moderated by fact-checking behavior and political ideology.

Based on existing literature, it is expected that higher exposure to political information on social media and fact-checking behavior are associated with a greater likelihood of perceiving climate change as a serious threat in Latin America. To test these hypotheses, this study employs multilevel logistic regression to analyze the interplay between these variables alongside relevant controls.

The next sections outline Latin America’s climate vulnerability and public perception trends, discuss the role of social media in shaping attitudes, describe the research design and methodology, present the results, and conclude with a discussion of their broader implications.

## 2. Latin America under heat

Climate change is rapidly restructuring Latin America's environmental, economic, and social landscapes. The increasing frequency of droughts, extreme weather events, and shifting agricultural patterns are exacerbating existing vulnerabilities and creating new ones. While the region is rich in natural resources, its susceptibility to climate-related disruptions calls for urgent and coordinated adaptation strategies. Addressing water security, promoting climate-resilient agricultural practices, and implementing sustainable urban planning will be critical in mitigating the worst effects of climate change for Latin Americans. The extent to which governments and communities take proactive measures today will determine the region’s ability to navigate the growing environmental challenges of the future.

It is clear that understanding how Latin American societies perceive climate change is essential in proposing effective policies and public engagement strategies, as historical and economic contexts have influenced the way climate issues have been prioritized in the region to this date. Throughout the 1980s, Latin America was grappling with economic turmoil, commonly referred to as “la década perdida". Due to escalating foreign debt, hyperinflation, and widespread military dictatorships, the region saw an average decline of 10-40% in GDP per capita between 1981 and 1989 (Lüders, 1991). Political instability, civil conflicts, and economic crises dominated national agendas, leaving little room for climate-related concerns. Consequently, systematic data collection on public perceptions of climate change remained scarce during this time. It was not until the mid-1990s that research on climate change perceptions in Latin America began gaining (some) traction.

Despite these historical data gaps, emerging research suggests that Latin America’s perception of climate change is molded by a combination of direct environmental experiences, economic vulnerabilities, and the historical political contexts above mentioned. While research on this topic remains limited compared to studies conducted in North America and Europe, available data indicates that the issue is widely recognized as a serious threat across the region. This heightened awareness could be largely driven by firsthand exposure to extreme weather events, shifting agricultural conditions, and resource scarcity (Magalhães & Magalhães, 2019; Ramos & Cavedon-Capdeville, 2017; Reyer et al., 2017). Farmers and rural populations, who are directly dependent on natural resources, are particularly attuned to climate variability. Additionally, demographic factors such as race, education, and gender play a role in shaping perceptions, influencing how different communities understand and respond to climate risks.

Unlike in some industrialized nations where climate skepticism is widespread, the majority of Latin Americans acknowledge the reality and severity of climate change. Surveys show that public concern is significantly higher than in regions where climate change has been politicized. According to LAPOP’s 2023 survey, an average of 78% of respondents from 17 Latin-American countries considered climate change a "very serious" issue. These figures contrast starkly with the United States, where only 39.6% of the population shares similar concerns, largely due to the politicization of climate science (Entman, 2018).

It can be argued that one of the reasons behind the heightened concern in Latin America is the direct experience of climate-related events. One theoretical framework that may apply to the region is the "differential vulnerability hypothesis", which proposes that marginalized communities are more concerned about climate change due to their increased exposure to environmental hazards. For example, Indigenous and Afro-descendant populations in Latin America often reside in areas that are disproportionately affected by climate-related disasters, such as coastal regions vulnerable to hurricanes and inland areas facing desertification (Finucane et al., 2000).

Different from developed countries, where climate change may seem like a distant, abstract or even fabricated issue, many Latin Americans witness its effects firsthand. Rising temperatures, prolonged droughts, stronger hurricanes, and flooding have become more frequent in the region, reinforcing the perception that climate change is an immediate and tangible threat (Baez et al., 2016). Additionally, climate-induced agricultural disruptions, water scarcity, and displacement contribute to the growing recognition of climate change as a pressing issue (Reyer et al., 2017).

Water availability, a cornerstone of food production and public health, is a key variable being affected by the rising global temperatures, responsible for accelerating evaporation rates, depleting surface water reserves, and contributing to increasingly volatile rainfall patterns (Mena et al., 2019). According to Heinke et al. (2019), even under optimistic scenarios that limit warming to below 2°C, an estimated 12% of Latin America's population will face severe water scarcity, with erratic climate patterns altering hydrological cycles in ways that jeopardize access to this clean water.

Droughts are becoming an increasingly common and severe issue, particularly in arid and semi-arid regions of Latin America. Between 2012 and 2016, some of the driest years on record were observed across Mexico, Central America, and parts of South America, demonstrating the intensification of prolonged dry spells (Magalhães & Magalhães, 2019).

The consequences of worsening droughts extend beyond water shortages and agricultural losses. According to Baenz et al. (2020), water scarcity is linked to migration patterns, particularly among younger populations. Migration rates are observed to increase with the severity of drought exposure, with an estimated four additional migrants per 1,000 individuals for every standard deviation increase in drought intensity. Central America, a region already experiencing high levels of emigration, has seen climate-driven migration rise significantly, particularly in countries such as Guatemala, Honduras, El Salvador, and Nicaragua (de Salles Cavedon-Capdeville et al., 2020). These trends hint that climate change is becoming a primary driver of human displacement in the region.

Parallel to slow-onset phenomena such as droughts, climate change is also fueling an increase in extreme weather events across Latin America. Hurricanes, floods, landslides, wildfires and storm surges are occurring with greater intensity and frequency, exacerbating both economic and human losses. Ramos & Cavedon-Capdeville (2017) estimate that between 1990 and 2013, a staggering 97% of recorded disasters in Latin America were linked to hydro-meteorological and climate-related events.

In the Caribbean, stronger hurricanes have become a dominant concern. The increased sea surface temperatures are intensifying tropical storms, leading to greater destruction in island nations already vulnerable to economic shocks. In South America, torrential rainfall and subsequent landslides threaten cities in mountainous regions, such as those in Colombia and Peru. Meanwhile, Argentina and Brazil face growing risks from wildfires, particularly in the Amazon and Pantanal biomes, where prolonged dry seasons create ideal conditions for large-scale forest loss.

It is expected that rising sea levels will also be a major concern for Latin America. Reguero et al. (2015) state that between 29 and 32 million people in the region live within 10 meters of current sea levels, placing them at substantial risk of climate-induced flooding. Some Caribbean nations, such as the Bahamas and Turks and Caicos Islands, have over 70% of their landmass below this elevation, making them exceptionally vulnerable to storm surges and long-term inundation. Even larger nations such as Mexico face challenges, with millions of residents in low-lying coastal areas.

Despite the dangers for the region’s population, research on climate change perceptions has focused predominantly on the agricultural sector. This concentration is unsurprising, as the agriculture quickly experiences the consequences of climate variability, including shifts in precipitation patterns, soil degradation, and increased pest infestations. Rising global temperatures, erratic precipitation patterns, and extreme weather events will increasingly disrupt agricultural yields, posing challenges for national economies dependent on exports (Abeldaño Zuñiga, Lima, & González Villoria, 2021). Unlike industrialized nations, where food shortages can often be mitigated through imports, many regions in Latin America face infrastructural and economic barriers that exacerbate the consequences of agricultural instability.

One of the most pressing concerns is soil degradation. Already, vast portions of Latin American croplands suffer from soil erosion, nutrient depletion, and desertification. According to Santibáñez and Santibáñez (2007), up to 45% of croplands in South America and 74% in Mesoamerica show signs of degradation, a situation that continues to deteriorate due to increased temperatures and shifting rainfall patterns. Similarly, Vieira et al. (2020) report that northeast Brazil, a region historically prone to droughts, faces heightened risks of desertification, jeopardizing staple crops such as corn and beans.

Coffee, a major economic driver for many nations in the region, faces an uncertain future due to warming temperatures, shifting precipitation patterns, and the spread of pests and plant diseases. Research indicates that by 2050, the land area suitable for coffee cultivation may shrink by up to 40%, with Brazil, the world's leading coffee exporter, expected to experience the most severe impacts (Laderach et al., 2010; Koh et al., 2020). Climate-induced threats such as leaf rust (Hemileia vastatrix) are predicted to spread southward, further decreasing yields and increasing production costs (Reyer et al., 2017).

But the economic effects of climate change are not limited to crops alone. Livestock production, a key component of many Latin American economies, is also at risk. Rising temperatures and prolonged droughts contribute to heat stress in cattle, reducing their productivity, reproductive rates, and overall health. Paraguay, a country heavily reliant on beef exports, is projected to experience a significant decline in cattle populations due to temperature increases of 2° to 3°C, leading to estimated losses of 16% to 27% in the sector (Reyer et al., 2017).

With both crop and livestock production facing mounting difficulties, the region's ability to maintain food security remains uncertain. One of the earliest studies in the region, conducted by Hansen et al. (2004), found that two-thirds of surveyed farmers in Argentina reported observing changes in climate variability, demonstrating an acute awareness of environmental shifts. Similarly, research by Barrucand et al. (2016) found that farmers’ perceptions of precipitation changes were heavily influenced by their direct experiences with extreme weather events such as droughts and floods.

But the differential vulnerability hypothesis and agricultural decline are not the only factors influencing peoples’ perceptions. Education also impacts climate change awareness. A comparative study across multiple countries, including Ecuador, the United States, Australia, and the United Kingdom, found a positive correlation between education levels and climate awareness (Crona et al., 2013). Higher levels of education are associated with increased access to climate information, scientific literacy, and overall engagement in environmental issues. However, the effectiveness of education in fostering climate concern varies depending on the accessibility of reliable information and the prevalence of misinformation.

In contrast to the United States, where climate change is a highly partisan issue, Latin American attitudes toward climate change appear to be less divided along ideological lines. While some studies suggest that left-leaning individuals are more likely to support environmental policies, the relationship between political ideology and climate skepticism is weaker in Latin America than in North America and Western Europe (Spektor et al., 2023). This may be due to the fact that environmental issues in Latin America have historically been framed as development challenges rather than ideological debates.

Nevertheless, as climate discourse becomes more prominent in the political arena, there is potential for increased polarization. In countries such as Brazil, where recent administrations have rolled back environmental protections, climate skepticism has begun to emerge among certain political factions. Understanding how political ideology intermingles with climate perceptions in Latin America will require further research as the issue gains salience in regional policymaking.

Although political polarization on climate change is less pronounced in Latin America compared to the United States, shifting political landscapes may alter public attitudes in the future. Expanding research efforts to better understand climate perceptions across diverse social groups in Latin America will be critical for designing effective climate policies and communication strategies.

## 3. Political Social Media and Climate Change Perception

The advent of social media has fundamentally altered the way information is disseminated, consumed, and interpreted. In the context of climate change, social media platforms such as Facebook, X (Twitter), Instagram, and WhatsApp have become central avenues for raising awareness, fostering discussions, and mobilizing political action (Diehl et al., 2024; Shah, 2024). However, these tools also serve as breeding grounds for misinformation, selective exposure, and ideological echo chambers, making their overall impact on climate change perception complex and multifaceted (Tyagi & Carley, 2021).

One of the most significant benefits of social media is its ability to rapidly spread scientific findings and urgent climate messages to a broad audience. Unlike traditional media, which relies on editorial oversight and structured broadcasting schedules, social media enables real-time information-sharing, often making it the first source of climate-related news for many users (Spektor, Fasolin, & Camargo, 2023).

Data from The AmericasBarometer, Latin American Public Opinion Project (LAPOP) for 17 countries in 2018 further illustrate the widespread role of social media in shaping public discourse. Table 1 presents the percentage of respondents who have an account on at least one social media platform.

<div style="text-align:center; font-weight:bold;">Table 1: Respondents with accounts on social media</div>
|                | Facebook | X (Twitter) | WhatsApp | One or more platforms |
|:--------------:|:--------:|:-----------:|:--------:|:---------------------:|
| Percentage     |  57.6%   |    8.97%    |   64.4%  |         70.6%         |
| Total          |  25459   |    25424    |   25506  |         25563         |
<div style=font-size:smaller;">Author's elaboration.</div><br>

Facebook and WhatsApp dominate the digital landscape in the analyzed countries, while Twitter remains less commonly used. More than 70% of the sample reported having an account on one or more social media platforms. Among these users, a substantial proportion actively engages with political content. Figure 1 highlights the percentage of social media users who seek political information daily or several times a week.

<div style="text-align:center; font-weight:bold;">Figure 1: Percentage of users who use social media to inform themselves about politics</div>

<div style="display: flex; justify-content: center;">
```{r fig1, fig.width = 10, fig.height = 5}
lp18 <- lp18 %>%
  mutate(pais = case_when(
    pais == "Argentina" ~ "ARG",
    pais == "Bolívia" ~ "BOL",
    pais == "Brasil" ~ "BRA",
    pais == "Chile" ~ "CHL",
    pais == "Colômbia" ~ "COL",
    pais == "Costa Rica" ~ "CRI",
    pais == "Rep. Domin." ~ "DOM",
    pais == "Equador" ~ "ECU",
    pais == "Guatemala" ~ "GTM",
    pais == "Honduras" ~ "HND",
    pais == "México" ~ "MEX",
    pais == "Panamá" ~ "PAN",
    pais == "Perú" ~ "PER",
    pais == "Paraguai" ~ "PRY",
    pais == "El Salvador" ~ "SLV",
    pais == "Uruguai" ~ "URY",
    pais == "Nicaragua" ~ "NIC",
    TRUE ~ pais 
  ))

face <- lp18 %>%
  gather("Type", "Value", 1) %>% 
  group_by(pais) %>%
  summarize(mean = mean(Value[!is.na(Value)])) %>%
  mutate(pais = fct_reorder(pais, mean)) %>% 
  ggplot(aes(mean * 100, pais)) +
  geom_point(size = 4, color = "blue", alpha = .7) +
  theme_bw(base_size = 13) +
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
  theme(
    plot.margin = unit(c(1.2, 1, 0, 0), "mm"),
    plot.caption = element_text(hjust = 0)
  ) +
  labs(x = "Facebook", y = "Country") +
  geom_segment(aes(xend = 0, y = pais, yend = pais),
               color = "blue", alpha = .7)


twit <- lp18 %>%
    gather("Type", "Value", 2) %>% 
    group_by(pais) %>%
    summarize(mean = mean(Value[!is.na(Value)])) %>%
    mutate(pais = fct_reorder(pais, mean)) %>% 
    ggplot(aes(mean*100, pais)) +
    geom_point(size = 4, color = "#0099ff", alpha = .7) +
    theme_bw(base_size = 13) +
    scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
    theme(plot.margin=unit(c(1.2,1,0,0),"mm")) +
    labs(x = "X (Twitter)", y = "") +
    geom_segment(aes(xend = 0, y = pais, yend = pais),
                 color = "#0099ff", alpha = .7)

what <- lp18 %>%
    gather("Type", "Value", 3) %>% 
    group_by(pais) %>%
    summarize(mean = mean(Value[!is.na(Value)])) %>%
    mutate(pais = fct_reorder(pais, mean)) %>% 
    ggplot(aes(mean*100, pais)) +
    geom_point(size = 4, color = "#009900", alpha = .7) +
    theme_bw(base_size = 13) +
    scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
    theme(plot.margin=unit(c(1.2,1,0,0),"mm")) +
    labs(x = "WhatsApp", y = "") +
    geom_segment(aes(xend = 0, y = pais, yend = pais),
                 color = "#009900", alpha = .7)

invisible(gridExtra::grid.arrange(face, twit, what, ncol = 3))
```
</div>

The data reveal some cross-country variations in social media usage for political purposes. In Bolivia, approximately 71% of Facebook users rely on the platform to stay informed about politics, the highest percentage in Latin America in 2018. For X, El Salvador leads, with 75% of its users utilizing the site for political updates. Meanwhile, Brazil ranks first for political engagement on WhatsApp, where about 50% of users turn to the app as a source of political information.

Social media has played a crucial role in democratizing access to climate knowledge, bridging gaps between experts and the general public. Previously, climate science was primarily disseminated through academic journals and news reports, limiting accessibility to those with specialized knowledge. Today, scientists, activists, and organizations use social media to communicate findings in more digestible formats, such as infographics, short videos, and interactive discussions, making climate science more engaging and understandable for a wider audience (Gómez-Casillas & Márquez, 2023). Therefore, it is hypothesized that:

*H1. High exposure to political information through social media increases the likelihood of agreement that climate change is a serious threat.*

Despite its potential as a tool for education and mobilization, social media is also notorious for facilitating the spread of misinformation. Unlike traditional news outlets, where journalistic integrity and fact-checking are usually standard practices, social media platforms operate with minimal content moderation, allowing misleading narratives to gain traction rapidly (Lewandowsky, Gignac, & Oberauer, 2013). Climate denialism, conspiracy theories, and pseudoscientific claims flourish in such an environment, often fueled by ideological biases and agenda-driven actors (Tyagi & Carley, 2021).

One of the key mechanisms through which misinformation spreads is the echo chamber effect — the tendency for social media users to engage primarily with content that aligns with their pre-existing beliefs while avoiding contradictory perspectives (Tyagi & Carley, 2021). Algorithm-driven content curation exacerbates this issue, as platforms prioritize user engagement over accuracy, often amplifying sensationalist or misleading information that generates strong emotional reactions. As a result, people already inclined toward climate skepticism may become further entrenched in their views, reducing the likelihood of changing their stance even when confronted with credible scientific evidence (Lewandowsky, Gignac, & Oberauer, 2013).

Given this reality, it is plausible that H1 may not hold uniformly across all users. Simply being exposed to social media does not necessarily lead to a greater recognition of climate change as a threat. Rather, the type — and quality — of content encountered and the degree to which individuals engage in critical evaluation likely mediate the relationship between social media use and climate concern.

Fact-checking has emerged as a crucial countermeasure to the spread of misinformation on social media, particularly concerning climate change. Organizations such as Science Feedback[^1] and other independent fact-checking initiatives play a key role in identifying and correcting false or misleading climate narratives. However, the effectiveness of these efforts depends on whether users actively engage with this content and trust the sources providing the corrections. Exposure to verified scientific sources, expert opinions, and climate advocacy campaigns helps reinforce the credibility of climate science, thereby fostering a stronger public commitment to climate action (Spektor, Fasolin, & Camargo, 2023).

[^1]: <https://science.feedback.org/>

*H2. Fact-checking behavior increases the likelihood of agreement with climate change concerns.*

If H2 holds, then those who actively engage in fact-checking should be less susceptible to such distortions, as they would be more likely to encounter and trust scientifically validated information. However, if fact-checking behavior is more common among those who already believe in climate change, then its effect may simply reflect pre-existing scientific trust rather than a causal driver of belief.

However, fact-checking alone is not always sufficient to overcome the cognitive biases that conditions how people process information. The backfire effect — where corrections to misinformation sometimes strengthen pre-existing beliefs — can limit the impact of fact-checking efforts, particularly among individuals who are ideologically predisposed to dismiss climate science. Additionally, the effectiveness of fact-checking is often constrained by the selective exposure phenomenon, where users tend to seek out and believe information that aligns with their worldview while disregarding countervailing evidence. In such cases, even when accurate information is made available, its reach and persuasive power may be diminished if individuals remain within insular digital environments that reinforce climate skepticism (Spektor, Fasolin, & Camargo, 2023).

This naturally leads to the role of political ideology in determining how social media influences climate change perceptions. In Latin America, as in other regions, political leanings serve as a lens through which people interpret climate-related content, informing whether they should trust the scientific consensus (Spektor, Fasolin, & Camargo, 2023). Studies assert that conservative-leaning users are more likely to be skeptical of climate change narratives, especially when their social media feeds are dominated by sources that downplay or dismiss environmental concerns. Conversely, progressive-leaning individuals tend to be more receptive to climate advocacy and scientific warnings, engaging more frequently with pro-environmental content (Gómez-Casillas & Márquez, 2023).

## 4. Research design

By utilizing data from the 2023 Latin American Public Opinion Project (LAPOP), this research examines how respondents’ engagement with political content on social media interacts with their demographic characteristics, political ideology, fact-checking behavior and their views on climate change. Given the complexity of digital information ecosystems, this study considers both the potential of social media to enhance public understanding of climate change and its capacity to reinforce misinformation and ideological divides.

The dataset comprises responses from 16,644 individuals across multiple Latin American countries[^2]. The survey is designed to be nationally representative within each participating country, allowing for generalizable inferences about climate attitudes in the region.

[^2]: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Dominican Republic, Ecuador, Guatemala, Honduras, Jamaica, Mexico, Panama, Peru, Paraguay, El Salvador and Uruguay.

The dependent variable is concern about climate change, operationalized as a binary measure indicating whether respondents perceive climate change as a serious threat to their country. The primary independent variables of interest are “social media exposure”, defined as whether respondents consume political content daily on social networking platforms; and fact-checking behavior, which examines whether verifying information found online in the past three months influences climate concern, given the prevalence of misinformation on digital platforms.

Demographic controls are incorporated to account for potential confounding effects. These include gender, age, education, income, and skin color. Additional control variables include political ideology, interest in politics, and preference for democracy. Political ideology is measured on a standardized scale, reflecting respondents' self-reported ideological leanings. Interest in politics captures the extent to which people actively follow political developments, while preference for democracy measures their support for democratic governance.

<div style="text-align:center; font-weight:bold;">Figure 2: Climate attitude across continuous variables</div>

```{r fig2}
ggplotly(
  m %>% 
    select(clima, age_s, educ_s, income_s, ideo_s, color_s) %>% 
    pivot_longer(
      cols = -clima,
      names_to = "variable",
      values_to = "value"
    ) %>% 
    mutate(variable = case_when(
      variable == "color_s" ~ "Skin color",
      variable == "age_s" ~ "Age",
      variable == "educ_s" ~ "Education",
      variable == "income_s" ~ "Income",
      variable == "ideo_s" ~ "Political ideology",
      TRUE ~ variable
    )) %>% 
    ggplot(aes(x = factor(clima), y = value, fill = factor(clima))) +
    geom_boxplot(alpha = .7) +
    facet_wrap(~ variable) +  # Remove scales = "free_y" for uniform y axes
    labs(
      x = "Climate Attitude",
      y = "Value",
      fill = "Climate Attitude"
    ) +
    scale_y_continuous(limits = c(-2, 4)) +  # Force y-axis limits
    scale_fill_okabe_ito() +
    theme_bw() +
    theme(
      panel.grid.minor.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      legend.position = "none",
      panel.spacing = unit(2, "lines")
    )
)
```
<div style=font-size:smaller;">Author's elaboration. Interactive plot: hover over the elements to reveal additional details. On the X axis: 0 = does not agree that climate change is a serious problem; 1 = agrees with the statement.</div><br>

To examine the relationship between exposure and climate concern, the analysis employs multilevel logistic regression models, which account for the hierarchical structure of the data, with individuals nested within countries. The use of country-level random intercepts accounts for unobserved national differences, such as variations in media landscapes, political institutions, and environmental policies, which may influence individual perceptions of climate change. Weights are applied to ensure that the findings remain representative of the surveyed populations. A series of progressively complex models are estimated to assess the influence of key predictors.

<div style="text-align:center; font-weight:bold;">Figure 3: Climate attitude across binary variables</div>

```{r fig3}
ggplotly(
  m %>% 
    select(
      clima, sexo, social_media, fact_check, interes_pol, pref_democ
    ) %>% 
    pivot_longer(
      cols = -clima,
      names_to = "variable",
      values_to = "value"
    ) %>%
    mutate(
      value = factor(value),
      variable = case_when(
        variable == "sexo" ~ "Gender",
        variable == "color_s" ~ "Skin color",
        variable == "interes_pol" ~ "Interest for politics",
        variable == "pref_democ" ~ "Preference for democracy",
        variable == "social_media" ~ "High exposure",
        variable == "fact_check" ~ "Fact check",
        TRUE ~ variable
      )
    ) %>%
    group_by(clima, variable, value) %>%
    summarise(count = n(), .groups = "drop") %>%
    group_by(clima, variable) %>%
    mutate(proportion = count / sum(count)) %>%
    ggplot(aes(
      x = factor(clima),
      y = proportion,
      fill = value,
      text = sprintf("Value: %s<br>Proportion: %.2f%%", value, proportion * 100)
    )) +
    geom_bar(stat = "identity", position = "fill", alpha = .7) +
    facet_wrap(~ variable) +
    labs(
      x = "Climate Attitude",
      y = "Proportion",
      fill = "Category"
    ) +
    scale_fill_okabe_ito() +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.5)) +
    theme_bw() +
    theme(
      legend.position = "none",
      panel.spacing = unit(2, "lines")
    ),
  tooltip = "text"
)
```
<div style=font-size:smaller;">Author's elaboration. Interactive plot: hover over the elements to reveal additional details. On the X axis: 0 = does not agree that climate change is a serious problem; 1 = agrees with the statement.</div><br>

The baseline model (M1) includes only demographic controls to establish a foundational understanding of how structural factors are related to climate concern. The second model (M2) introduces social media exposure and fact-checking behavior to evaluate the interplay of digital engagement and climate concern. The third model (M3) expands upon this by incorporating political ideology, interest in politics, and democratic preference, recognizing that climate attitudes are often shaped by broader political and institutional beliefs. Finally, the fourth model (M4) includes an interaction between individuals who actively engage in both social media use and fact-checking with ideology, testing whether political orientation moderates the relation of fact-checked digital engagement with climate concern.

## 5. Results

Table 2 exposes the results. Gender, age, education, income, and skin color consistently play a role in conditioning climate change concern across all models. Women are significantly more likely than men to perceive climate change as a serious issue (β = -19.06, p \< 0.001, M3), suggesting that men, on average, are less likely to express strong concern about climate change.

<div style="text-align:center; font-weight:bold;">Table 2: Multilevel logistic regression models</div>
```{r table2, results="asis"}
custom_names <- c(
  "(Intercept)" = "Intercept",
  "sexo" = "Gender",
  "age_s" = "Age",
  "color_s" = "Skin color",
  "educ_s" = "Education",
  "income_s" = "Income",
  "social_media" = "High social media exposure",
  "fact_check" = "Fact-check behavior",
  "ideo_s" = "Political ideology",
  "interes_pol" = "Interest in politics",
  "pref_democ" = "Preference for democracy",
  "freq_fact_checkda" = "Exposure & Fact-check",
  "freq_fact_checkda:ideo_s" = "Exposure & Fact-check × Ideology"
)

texreg::htmlreg(
  list(m1, m2, m3, m4),
  digits = 2,
  override.coef = lapply(
    list(m1, m2, m3, m4),
    function(model) (exp(fixef(model)) - 1) * 100
  ),
  custom.model.names = c("M1", "M2", "M3", "M4"),
  custom.coef.names = custom_names,
  include.rsquared = FALSE,
  include.adjrs = FALSE,
  include.loglik = FALSE,
  include.aic = FALSE,
  include.bic = FALSE,
  include.deviance = FALSE,
  include.re.var = FALSE,
  include.groups = FALSE,
  include.random = FALSE,
  include.thresholds = F,
  include.variance = F,
  include.events = F,
  include.proj.stats = F,
  include.dev.expl = F,
  include.dispersion = F,
  include.gcv = F,
  include.overidentification = F,
  include.obj.fcn = F,
  include.df = F,
  include.nobs = TRUE
)
```
<div style=font-size:smaller;">Author's elaboration. Coefficients presented as percentage change in odds ratio.</div><br>

Age is positively associated with climate concern (β = 23.56, p \< 0.001, M3), meaning older individuals are more likely to recognize climate change as a severe problem. Education also has a robust positive correlation with climate concern. Highly educated people are significantly more likely to express concern (β = 30.70, p \< 0.001, M3), hinting that greater access to information and scientific literacy contribute to awareness of climate issues. Income, on the other hand, exhibits a negative relationship with climate concern (β = -14.54, p \< 0.01, M3), which could point towards a perception that wealth can insulate from the effects of global warming.

Skin color is a weaker predictor but remains statistically significant (β = 4.79, p \< 0.05, M3), denoting that increases in skin color are, on average, associated with greater concern for climate change. Given the socioeconomic and racial inequalities in Latin America, this may reflect differential vulnerability to environmental risks.

From Model 2 onwards, the role of obtaining political information through social media and fact-checking behavior is introduced. While high exposure has a small positive correlation with climate concern (β = 2.23, M3), it does not reach statistical significance, suggesting that merely consuming political content online is not a strong determinant of climate attitudes.

In contrast, fact-checking behavior is strongly correlated with climate concern (β = 23.37, p \< 0.001, M3). Respondents who verify the accuracy of information at least once every three months are significantly more likely to perceive climate change as a serious problem. This implies that exposure to credible sources mitigates misinformation and reinforces scientific consensus — or, alternatively, that those already inclined to trust the science and believe in the dangers of global warming are more predisposed to fact-checking behavior.

Starting from Model 3, political ideology, interest in politics, and democratic preference are included to assess the role of ideological orientation in climate perceptions. Political ideology is a strong and significant predictor (β = -14.87, p \< 0.001, M3), indicating that people with more conservative beliefs are less likely to be concerned about climate change.

Political interest shows a weaker, non-significant connection (β = 10.49, M3), conveying that general engagement with political affairs does not necessarily translate into heightened climate concern. In contrast, preference for democracy is strongly associated with climate concern (β = 32.64, p \< 0.001, M3), denoting that surveyed people who support democratic governance are more likely to acknowledge climate risks.

<div style="text-align:center; font-weight:bold;">Figure 4: Predicted probability of agreement across predictors</div>

<iframe src="https://marisguia.shinyapps.io/adapta/" style="width: 120%; height: 540px; border: 0;"></iframe>

<div style=font-size:smaller;">Author's elaboration. Instructions: 1) Use the "Select conditioning variable" dropdown to choose the predictor displayed on the x-axis. 2) Use the "Select slider variable" dropdown to choose a variable that dynamically changes through the animation. 3) Use the slider at the bottom to control the animation. The plot shows the predicted probability of the outcome based on the selected variables. Other predictors remain constant at their default values.</div><br>

Finally, Model 4 includes an interaction term between fact-checking behavior, social media exposure and political ideology, and can be visualized in the interactive Figure 5. The coefficient for political ideology (β = −13.51, p \< 0.001, M4) connotes that, among respondents outside the conjunction of high social media exposure and fact-check behavior, a one standard deviation increase in conservatism is associated with a 13.51% decrease in the odds of perceiving climate change as a serious danger.

<div style="text-align:center; font-weight:bold;">Figure 5: Coefficients, Model 4</div>

```{r fig5}
t_m4 <- tidy(m4, conf.int = TRUE, conf.method = "Wald", effects = "fixed") %>%
  mutate(
    OR = exp(estimate),
    OR_low = exp(conf.low),
    OR_high = exp(conf.high),
    perc_change = (OR - 1) * 100,
    color = case_when(
      p.value < 0.05 & perc_change > 0 ~ "deepskyblue4",
      p.value < 0.05 & perc_change < 0 ~ "darkgoldenrod2",
      TRUE ~ "grey50"
    ),
    term = recode(term,
  "(Intercept)" = "Intercept",
  "sexo" = "Gender",
  "age_s" = "Age",
  "color_s" = "Skin color",
  "educ_s" = "Education",
  "income_s" = "Income",
  "social_media" = "High social media exposure",
  "fact_check" = "Fact-check behavior",
  "ideo_s" = "Political ideology",
  "interes_pol" = "Interest in politics",
  "pref_democ" = "Preference for democracy",
  "freq_fact_checkda" = "Exposure & Fact-check",
  "freq_fact_checkda:ideo_s" = "Exposure & Fact-check × Ideology"
    )
  ) %>%
  filter(term != "Intercept")


p1_m4 <- t_m4 %>%
  ggplot(aes(
    x = perc_change,
    y = reorder(term, perc_change),
    text = sprintf("Percentage change: %.2f%%", perc_change)
  )) + 
  geom_point(aes(color = color), size = 2, alpha = 0.7, show.legend = FALSE) +  
  geom_errorbarh(aes(
    xmin = (OR_low - 1) * 100,
    xmax = (OR_high - 1) * 100,
    color = color
  ), height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  scale_color_identity() + 
  labs(
    x = "Percentage change in the odds of agreement", 
    y = NULL
  ) +
  theme_bw() +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank()
  )

ggplotly(p1_m4, tooltip = "text") %>% 
  layout(showlegend = FALSE)
```
<div style=font-size:smaller;">Author's elaboration. Coefficients presented as percentage change in odds ratio. Interactive plot: hover over the elements to reveal additional details. In blue: statistically significant positive coefficients. In orange: statistically significant negative coefficients.</div><br>

The coefficient for the conjunction fact-checked exposure (β = 16.08, p \< 0.01) implying that, for individuals at the mean level of political ideology, high exposure to social media alongside fact-checking behavior is associated with a 16.08% increase in the odds of perceiving climate change as a serious danger.

The interaction term (β = −5.89) shows that, among those with high exposure and fact-checking behavior, each one standard deviation increase in political conservatism is associated with an additional 5.89% decrease in the odds of agreeing that climate change is a serious danger. However, the lack of statistical significance (p \> 0.05) revealing that this moderating relation is not robust.

## 6. Discussion

By examining the influence of demographic, political, and informational factors, this research seeks to contribute to a deeper understanding of how digital media interacts with public attitudes toward climate change in a region particularly vulnerable to its effects. In doing so, it builds upon previous studies on climate perception and media influence, while addressing gaps in research specific to Latin America.

The results confirm several well-documented trends while also highlighting new complexities in how digital information consumption interacts with ideological orientations. Although high exposure to political content on social media was initially expected to influence climate concern, it has been shown that, alone, this variable does not have a significant explanatory power, leading to the conclusion that digital information ecosystem, which pose that social media functions as both a source of valuable information and a breeding ground for misinformation, play a significant role. While platforms can facilitate rapid dissemination of scientific findings, it can also reinforce ideological echo chambers in which misinformation circulates freely.

One of the strongest predictors of climate concern is political ideology. Consistent with previous research, individuals with more conservative beliefs are significantly less likely to view climate change as a significant issue. This trend aligns with broader global patterns in which conservative ideology is often associated with climate skepticism, a phenomenon attributed to ideological resistance to regulatory interventions, distrust in scientific institutions, and alignment with economic interests opposed to aggressive climate policies.

Despite the strong association between conservatism and lower climate concern, the study finds that actively fact-checking content has a substantial positive correlation with climate perceptions. Individuals who verify information are significantly more likely to acknowledge the dangers of climate change — or vice-versa. However, the interaction between political ideology and high exposure alongside fact-checking does not reach statistical significance. This suggests that while access to credible information walk side-by-side with climate concern, ideological predispositions remain a powerful filter through which individuals interpret political content online. This raises important questions about the effectiveness of fact-checking strategies in highly polarized environments. While the action could possibly enhance climate awareness, its impact are limited if individuals selectively engage with sources that reinforce their worldview.

The strong positive correlation of fact-checking behavior highlights the importance of digital literacy and access to reliable sources outside social media in combating misinformation and strengthening public trust in scientific consensus. However, a key question remains unresolved: the direction of causality between fact-checking habits and agreement that climate change is a serious problem. The findings clearly indicate that individuals who engage in fact-checking are more likely to recognize the severity of global warming, but the nature of this relationship remains ambiguous.

One possibility is that fact-checking serves as a corrective mechanism that actively shifts individuals’ climate perceptions. Exposure to verified information may counteract misinformation, reinforce scientific consensus, and lead to greater acceptance of climate change as a serious threat. This illustrates that promoting fact-checking actions could be an effective strategy to increase public concern about climate change. If this is the case, interventions aimed at encouraging media literacy and critical engagement with sources could play a crucial role in shaping climate attitudes.

Alternatively, it is also plausible that the relationship operates in the opposite direction — that individuals who already accept climate science and perceive global warming as a pressing issue are more motivated to fact-check the information they find. Those who strongly believe in the severity of the issue may be more inclined to verify claims, engage with credible sources, and avoid misinformation. In this scenario, fact-checking would not be the cause of climate concern but rather a consequence of pre-existing attitudes. If this interpretation is correct, it would suggest that fact-checking may do little to shift the views of climate skeptics, as those who distrust climate science may also be less likely to engage in fact-checking behavior in the first place.

A third possibility is that the relationship is bidirectional, with fact-checking and climate concern reinforcing one another over time. Individuals who begin fact-checking may become more convinced of the urgency of climate change, leading them to seek out even more fact-based information. Conversely, those who already acknowledge climate change as a major issue may increasingly engage in fact-checking to confirm their beliefs and reject misinformation.

To disentangle these possibilities, future studies should employ experimental or longitudinal designs. Controlled experiments could assess whether exposure to fact-checked climate content causes individuals to become more concerned about climate change, while panel data could track whether changes in climate concern predict increased fact-checking behavior over time. Understanding the causal direction of this relationship is crucial for designing effective interventions: if fact-checking drives climate concern, efforts should focus on increasing fact-checking habits; if climate concern leads to fact-checking, then enhancing climate education may be the more effective strategy.

The findings presented expose the need for more effective climate communication strategies that account for both ideological predispositions and the digital information environment. While fact-checking could increase the likelihood of climate concern, its impact appear constrained by selective exposure and motivated reasoning. Therefore, simply increasing the availability of verified information may not be enough to shift perceptions, particularly among individuals predisposed to climate skepticism.

Given the strong influence of ideology on climate concern, communication strategies should tailor messages to different ideological groups rather than relying on a one-size-fits-all approach. Framing climate change in terms of economic benefits, national security, or public health can make climate messages more persuasive to conservative audiences. Instead of emphasizing environmental degradation alone, advocates and policymakers might consider highlighting how climate action can lead to job creation, energy independence, or public health improvements.

Beyond messaging strategies, policymakers must also address the role of social media in disseminating scientific (mis)information. The fact that consuming political content through social media, by itself, does not influence climate concern reinforces the idea that platforms function as both sources of credible information and fake news. This stresses the need for platform accountability measures, such as increasing transparency in content algorithms, prioritizing evidence-based climate content, and actively reducing the visibility of misleading narratives. Alas, recent policy shifts by major platforms expose a troubling trend toward reduced moderation, highlighting the growing challenge of combating misinformation in an increasingly deregulated digital environment.

These findings offer insights that extend beyond Latin America, as similar dynamics of ideological filtering, misinformation, and selective exposure constrain climate perceptions globally. While the region exhibits elevated levels of climate concern compared to regions such as North America, the increasing politicization of climate discourse suggests that ideological divides may deepen over time. Future research should explore how these patterns evolve in diverse sociopolitical contexts, particularly in emerging economies that face comparable environmental and digital challenges.

Addressing climate misinformation and skepticism will require a multi-faceted approach that combines evidence-based communication strategies with systemic changes in how climate information is disseminated and consumed. As misinformation continues to interfere with public discourse, fostering a more informed and engaged public will be essential for advancing science-based climate action in the years to come.

## References

Abeldaño Zuñiga, R. A.; Lima, G. N. & González Villoria, A. M. (2021). Impact of slow-onset events related to climate change on food security in Latin America and the Caribbean. Current Opinion in Environmental Sustainability, 50, 215–224.

Azócar, G., Billi, M., Calvo, R., Huneeus, N., Lagos, M., Sapiains, R., & Urquiza, A. (2020). Climate change perception, vulnerability, and readiness: inter-country variability and emerging patterns in Latin America. Journal of Environmental Studies and Sciences.

Baez, J.; Caruso, G.; Mueller, V. & Niu, C. (2016). Droughts augment youth migration in Northern Latin America and the Caribbean. Climatic Change, 140(3-4), 423–435.

Barrucand, M. G.; Giraldo Vieira, C. & Canziani, P. O. (2016). Climate change and its impacts: perception and adaptation in rural areas of Manizales, Colombia. Climate and Development, 9(5), 415–427.

Crona, B.; Wutich, A.; Brewis, A. & Gartin, M. (2013). Perceptions of climate change: Linking local and global perceptions through a cultural knowledge approach. Climatic Change, 119(2), 519–531.

Dasgupta, S. & De Cian, E. (2018). The influence of institutions, governance, and public opinion on the environment: Synthesized findings from applied econometrics studies, Energy Research & Social Science, Volume 43, 2018, Pages 77-95.

De Salles Cavedon-Capdeville, F.; Ramos, E. P.; Zamur, A. C.; Serraglio, D. A.; Odriozola, I.; de Moura Pallone, L.; Damacena, F. D.; Yamamoto, L. & Pinheiro, G. M. (2020). Climate change, extreme events and human mobility in Latin America: Exploring the links through national laws and policies. Climate Change Management, 679–700.

Diehl, T.; Huber, B.; Zúñinga, H. D. & Liu, J. (2024). Social Media and Beliefs about Climate Change: A Cross-National Analysis of News Use, Political Ideology, and Trust in Science. International Journal of Public Opinion Research. doi:10.1093/ijpor/edz040.

Egan, P. J., & Mullin, M. (2017). Climate Change: US Public Opinion. Annu. Rev. Polit. Sci. 2017. 20:23.1–23.19.

Entman, L. (2018). Climate change concerns much higher in Latin America, Caribbean than U.S.; Canada. Vanderbilt University.

Evans, C. Q., & Zechmeister, E. J. (2018). Education and Risk Assessments Predict Climate Change Concerns in Latin America and the Caribbean. Latin American Public Opinion Project. Insights Series #129. Vanderbilt University.

Fairbrother, M. (2022). Public opinion about climate policies: A review and call for more studies of what people want. PLOS Clim 1(5): e0000030.

Finucane, M. L.; Slovic, P.; Mertz, C. K.; Flynn, J. & Satterfield, T. A. (2000). Gender, race, and perceived risk: The 'white male' effect. Health, Risk & Society, 2(2), 159–172.

Gómez-Casillas, A. & Márquez, V. G. (2023). The effect of social network sites usage in climate change awareness in Latin America. Population and Environment 45, 7 (2023).

González-Hernández, D. L.; Meijles, E. W. & Vanclay, F. (2019). Household Barriers to Climate Change Action: Perspectives from Nuevo Leon, Mexico. Sustainability, 11(15), 4178–4192.

Hansen, J.; Marx, S. & Weber, E. (2004). The Role of Climate Perceptions, Expectations, and Forecasts in Farmer Decision Making: The Argentine Pampas and South Florida. International Research Institute for Climate Prediction, 1, 1–55.

Heinke, J.; Müller, C.; Lannerstad, M.; Gerten, D. & Lucht, W. (2019). Freshwater resources under success and failure of the Paris climate agreement. Earth System Dynamics, 10(2), 205–217.

Koh, I.; Garrett, R.; Janetos, A. & Mueller, N. D. (2020). Climate risks to Brazilian coffee production. Environmental Research Letters, 15(10), 104015.

Laderach, P.; Lundy, M.; Jarvis, A.; Ramirez, J.; Portilla, E. P.; Schepp, K. & Eitzinger, A. (2010). Predicted impact of climate change on coffee supply chains. Climate Change Management, 703–723.

Lewandowsky, S.; Gignac, G. E. & Oberauer, K. (2013). The Role of Conspiracist Ideation and Worldviews in Predicting Rejection of Science. PLoS ONE 8(10): e75637.

Lüders, R. J. (1991). The 1980s: Economic Revolution in Latin America, Continuing Development in Asia. Asean Economic Bulletin, 8(1), 1–14.

Magalhães, A. R. & Magalhães, M. C. (2019). Drought preparedness and livelihood implications in developing countries: What are the options? Latin America and Northeast Brazil. Drought Challenges, 55–66.

Mena, D.; Solera, A.; Restrepo, L.; Pimiento, M.; Cañón, M. & Duarte, F. (2019). An analysis of unmet water demand under climate change scenarios in the Gualí River Basin, Colombia, through the implementation of Hydro-BID and WEAP hydrological modeling tools. Journal of Water and Climate Change, 12(1), 185–200.

Ramos, E. P. & Salles Cavedon-Capdeville, F. (2017). Regional responses to climate change and migration in Latin America. Research Handbook on Climate Change, Migration and the Law, 262–287.

Reguero, B. G.; Losada, I. J.; Díaz-Simal, P.; Méndez, F. J. & Beck, M. W. (2015). Effects of climate change on exposure to coastal flooding in Latin America and the Caribbean. PLOS ONE, 10(7), 1–19.

Reyer, C. P. O.; Adams, S.; Albrecht, T.; Baarsch, F.; Boit, A.; Canales Trujillo, N.; Cartsburg, M.; Coumou, D.; Eden, A.; Fernandes, E.; Langerwisch, F. & Marcus, R. (2017). Climate change impacts in Latin America and the Caribbean and their implications for development. Regional Environmental Change, 16(6), 1601–1621.

Santibáñez, F. & Santibáñez, P. (2007). Trends in land degradation in Latin America and the Caribbean, the role of climate change. Climate and Land Degradation, 65–81.

Shah, S. S. (2024). The Role of Social Media in Shaping Public Opinion on Environmental Issues. Premier Journal of Environmental Science.

Spektor, M.; Fasolin, G. N. & Camargo, J. (2023). Climate change beliefs and their correlates in Latin America. Nature Communications, 14, 7241.

Tyagi, A. & Carley, K. M. (2021). Climate Change Conspiracy Theories on Social Media. arXiv preprint arXiv:2107.03318.

Vieira, R. M.; Tomasella, J.; Barbosa, A. A.; Martins, M. A.; Rodriguez, D. A.; Rezende, F. S.; Carriello, F. & Santana, M. D. (2020). Desertification risk assessment in Northeast Brazil: Current trends and future scenarios. Land Degradation & Development, 32(1), 224–240.
